---
title: "Project"
subtitle: "ECON 21130"
author: "Raymond Han"
date: "3/22/17"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(doBy)
```

```{r load, message=FALSE}
require(kableExtra)
require(ggplot2)
require(texreg)
require(readstata13) #to install, run install.packages("readstata13")
require(sandwich)
require(lmtest)
require(dplyr)
require(poweRlaw)
options(knitr.table.format = "html") 
```

# 3.1 Proxying for Political Activism
```{r, results = 'asis'}
set.seed(60356549)
iter=20
p  = list(phi = 10,theta=1,beta=1, rho=0.95) # parameters
N=100000  # size of the simulation
K=50 # number of groups
J=50 # number of areas

coefs = data.table(i=1:iter)
for (i in 1:iter){

data = data.table(i=1:N,X=rnorm(N,mean=0,sd=1),eps=rnorm(N,mean=0,sd=1))
#assign groups (group sizes drawn from an exponential distribution)
data <- data[,k := ceiling(rexp(.N,rate = .05))]
data <- data[k>K,k := K]
#assign areas (area drawn from an exponential distribution, with probability rho next arrival in same group lives in same area)
data <- data[,j := {
  r = rep(0,.N)
  r[1] = ceiling(rexp(1,rate = .05))
  for (i in 2:.N) {
    if (runif(1)<p$rho){
    r[i] = r[i-1]
    }else{
    r[i] = ceiling(rexp(1,rate = .05))
    }
  }
  r
},k]
data <- data[j>J,j := J]

#assign neighborhood level shocks (normal)
data <- data[,gamma := rnorm(n=1,mean=0,sd=.2), j]
#assign group level shocks (normal)
data <- data[,delta := rnorm(n=1,mean=0,sd=.2), k]

#group latent political activity 
data <- data[,pi := p$beta*mean(X)+delta, k]

#ethnic concentration
data <- data[,group_size :=.N , k]
data <- data[,area_size :=.N , j]
data <- data[,e :=log((.N/area_size)/(group_size/N)) , by="k,j"]
data <- data[,epi := e*pi]

#voting decision
Rmean = mean(p$phi*data[,e]*data[,pi] + p$theta*data[,e] + p$beta*data[,X] + data[,delta] + data[,gamma] + data[,eps])
data <- data[,Rtilde := p$phi*e*pi + p$theta*e + p$beta*X + delta + gamma + eps]
data <- data[,R := (p$phi*e*pi + p$theta*e + p$beta*X + delta + gamma + eps)>Rmean]

#national voting rate
data <- data[,voterate:=mean(R), k]

#OLS fit
fit = lm(R ~ e:voterate + e + X + factor(j) + factor(k), data)
coefs <- coefs[i,phi := coef(fit)["e:voterate"]]
coefs <- coefs[i,theta := coef(fit)["e"]]
coefs <- coefs[i,beta := coef(fit)["X"]]

#logit fit
#fit2 = glm(R ~ e:voterate + e + X + factor(j) + factor(k), data ,family = binomial(link = "logit"))
#summary(fit2)
}
print(paste0('phi:', mean(coefs[,phi]), 'sd:', sd(coefs[,phi])))
print(paste0('theta:', mean(coefs[,theta]), 'sd:', sd(coefs[,theta])))
print(paste0('beta:', mean(coefs[,beta]), 'sd:', sd(coefs[,beta])))
```

Note that our estimate of phi is a bit off. We need to correct using the formula $\phi = \frac{\hat\phi}{1-\hat\phi\overline{e}}$.
```{r}
phi_adj = mean(coefs[,phi])/(1-mean(coefs[,phi])*mean(data[,e]))
print(paste0('phi (adjusted):', phi_adj))
```


Now suppose that some ethnic groups are more clustered than others, i.e. they have higher $\rho$. It is especially problematic is $\rho$ is a function of $\pi_k$. That is, if groups which are more politically active are also more (or less) clustered. Simulating this dependency:

```{r, results = 'asis'}
set.seed(60356549)
iter=20
p  = list(phi = 10,theta=1,beta=1, rho=0.95) # parameters
N=100000  # size of the simulation
K=50 # number of groups
J=50 # number of areas

coefs = data.table(i=1:iter)
for (i in 1:iter){

data = data.table(i=1:N,X=rnorm(N,mean=0,sd=1),eps=rnorm(N,mean=0,sd=1))
#assign groups (group sizes drawn from an exponential distribution)
data <- data[,k := ceiling(rexp(.N,rate = .05))]
data <- data[k>K,k := K]
#assign group level shocks (normal)
data <- data[,delta := rnorm(n=1,mean=0,sd=.2), k]
#group latent political activity 
data <- data[,pi := p$beta*mean(X)+delta, k]

#generate clustering parameter
data <- data[,rho_k := .95 + 0.25*pi]
data <- data[rho_k>0.99, rho_k :=0.99]

#assign areas (area drawn from an exponential distribution, with probability rho next arrival in same group lives in same area)
data <- data[,j := {
  r = rep(0,.N)
  r[1] = ceiling(rexp(1,rate = .05))
  for (i in 2:.N) {
    if (runif(1)<mean(rho_k)){
    r[i] = r[i-1]
    }else{
    r[i] = ceiling(rexp(1,rate = .05))
    }
  }
  r
},k]
data <- data[j>J,j := J]

#assign neighborhood level shocks (normal)
data <- data[,gamma := rnorm(n=1,mean=0,sd=.2), j]


#ethnic concentration
data <- data[,group_size :=.N , k]
data <- data[,area_size :=.N , j]
data <- data[,e :=log((.N/area_size)/(group_size/N)) , by="k,j"]
data <- data[,epi := e*pi]

#voting decision
Rmean = mean(p$phi*data[,e]*data[,pi] + p$theta*data[,e] + p$beta*data[,X] + data[,delta] + data[,gamma] + data[,eps])
data <- data[,R := (p$phi*e*pi + p$theta*e + p$beta*X + delta + gamma + eps)>Rmean]
data <- data[,Rtilde := p$phi*e*pi + p$theta*e + p$beta*X + delta + gamma + eps]

#national voting rate
data <- data[,voterate:=mean(R), k]

#OLS fit
fit = lm(R ~ e:voterate + e + X + factor(j) + factor(k), data)
coefs <- coefs[i,phi := coef(fit)["e:voterate"]]
coefs <- coefs[i,theta := coef(fit)["e"]]
coefs <- coefs[i,beta := coef(fit)["X"]]

#logit fit
#fit2 = glm(R ~ e:voterate + e + X + factor(j) + factor(k), data ,family = binomial(link = "logit"))
#summary(fit2)
}
print(paste0('phi:', mean(coefs[,phi]), 'sd:', sd(coefs[,phi])))
print(paste0('theta:', mean(coefs[,theta]), 'sd:', sd(coefs[,theta])))
print(paste0('beta:', mean(coefs[,beta]), 'sd:', sd(coefs[,beta])))
```
Performing the same correction now yields:
```{r}
phi_adj = mean(coefs[,phi])/(1-mean(coefs[,phi])*mean(data[,e]))
print(paste0('phi (adjusted):', phi_adj))
```

# 3.2 Differential Selection

```{r, results = 'asis'}
set.seed(60356549)
iter=20
p  = list(phi = 10,theta=1, beta=1, rho=0.95, theta1=2, theta2=1, a = 1) # parameters
N=10000  # size of the simulation
K=50 # number of groups
J=50 # number of areas

coefs = data.table(i=1:iter)
coefs2 = data.table(i=1:iter)
for (i in 1:iter){

data = data.table(i=1:N,X=rnorm(N,mean=0,sd=1),eps=rnorm(N,mean=0,sd=1))
#assign groups (group sizes drawn from an exponential distribution)
data <- data[,k := ceiling(rexp(.N,rate = .05))]
data <- data[k>K,k := K]
#assign areas (area drawn from an exponential distribution, with probability rho next arrival in same group lives in same area)
data <- data[,j := {
  r = rep(0,.N)
  r[1] = ceiling(rexp(1,rate = .05))
  for (i in 2:.N) {
    if (runif(1)<p$rho){
    r[i] = r[i-1]
    }else{
    r[i] = ceiling(rexp(1,rate = .05))
    }
  }
  r
},k]
data <- data[j>J,j := J]

#assign neighborhood level shocks (normal)
data <- data[,gamma := rnorm(n=1,mean=0,sd=.2), j]
#assign group level shocks (normal)
data <- data[,delta := rnorm(n=1,mean=0,sd=.2), k]

#group latent political activity 
data <- data[,pi := p$beta*mean(X)+delta, k]

#ethnic concentration
data <- data[,group_size :=.N , k]
data <- data[,area_size :=.N , j]
data <- data[,A := rnorm(.N,mean=0,sd=.5)]
data <- data[,B := rnorm(.N,mean=0,sd=.5)]
data <- data[,e :=  p$a*pi*A + B]
data <- data[,epi := e*pi]

#voting decision
Rmean = mean(p$phi*data[,e]*data[,pi] + p$theta*data[,e] + p$beta*data[,X] + data[,delta] + data[,gamma] + data[,A] + data[,eps])
data <- data[,R := (p$phi*e*pi + p$theta*e + p$beta*X + delta + gamma + A + eps)>Rmean]
data <- data[,Rtilde := p$phi*e*pi + p$theta*e + p$beta*X + delta + gamma + eps]
data <- data[,Rtilde2 := p$phi*e*pi + p$beta*X + delta + gamma + p$theta1*A + p$theta2*B + eps]

#national voting rate
data <- data[,voterate:=mean(R), k]

#OLS fit
#no differential selection
fit = lm(Rtilde ~ e:pi + e + X + factor(j) + factor(k), data)
coefs <- coefs[i,phi := coef(fit)["e:pi"]]
coefs <- coefs[i,theta := coef(fit)["e"]]
coefs <- coefs[i,beta := coef(fit)["X"]]
#differential selection
fit2 = lm(Rtilde2 ~ e:pi + e + X + factor(j) + factor(k), data)
coefs2 <- coefs2[i,phi := coef(fit2)["e:pi"]]
coefs2 <- coefs2[i,theta := coef(fit2)["e"]]
coefs2 <- coefs2[i,beta := coef(fit2)["X"]]

#logit fit
#fit2 = glm(R ~ e:voterate + e + X + factor(j) + factor(k), data ,family = binomial(link = "logit"))
#summary(fit2)
}
print("No Differential Selection")
print(paste0('phi:', mean(coefs[,phi]), 'sd:', sd(coefs[,phi])))
print(paste0('theta:', mean(coefs[,theta]), 'sd:', sd(coefs[,theta])))
print(paste0('beta:', mean(coefs[,beta]), 'sd:', sd(coefs[,beta])))
print("Differential Selection")
print(paste0('phi2:', mean(coefs2[,phi]), 'sd:', sd(coefs2[,phi])))
print(paste0('theta2:', mean(coefs2[,theta]), 'sd:', sd(coefs2[,theta])))
print(paste0('beta2:', mean(coefs2[,beta]), 'sd:', sd(coefs2[,beta])))
```